### 2021-04-27 input/related_work.tex
done, todo 10 pages

Content indexing services in geo-distributed infrastructures allow
\processes to retrieve specific content while leveraging the
advantages of replication. These systems mostly rely on dedicated
location services host by possibly remote third-party \processes~\REF;
and cutting the middleman requires that each \process maintains its
own index in a decentralized fashion~\REF. This section reviews these
approaches.

@@

\item [Broadcast:]
The opposite approach consists in hosting the index directly on the
nodes, avoiding any prior request to access a content.
\underline{N}amed \underline{D}ata \underline{N}etworking
(NDN)~\cite{nlsr} broadcasts information about cache updates to all nodes in the
system. Having the entire knowledge of all the
replica locations along with distance information carried into
messages, each node can easily determine where the closest copy of a
given object resides, without contacting any remote node.  Similarly,
one could use a
\underline{C}onflict-\underline{F}ree \underline{R}eplicated
\underline{D}atatype (CRDT) for set data structures, for
example~\cite{shapiro2011crdts}. Yet both solutions inherently imply
that every node will eventually receive all messages, contrary to \NAME.

\item [Membership protocols:]
At first glance, membership protocols~\cite{t-man}
would appear to provide suitable abstractions to create a
scope-related partitioning, as proposed in this paper. Such protocols
usually rely on gossip mechanisms, implying contacts with random nodes
that can be far away in the physical topology. 
They are mostly implemented by modifying the
neighboring of a given node according to a certain metric in a logical
overlay. On the contrary,  \NAME  does not aim at building any overlay, as
it only relies on the physical topology so the neighbors of a given node
are not continuously modified. These protocols are usually
cycle-based, meaning that they impose a constant load on the network
traffic, even when the system state does not change. \NAME only generates traffic upon system changes.

\item [Timeouts:]
Solutions that periodically advertise their
cache content~\cite{garcia-lopez, hemmati2015namebased} also
incur an overhead even in quiet contexts without any update.
Moreover, they necessarily rely on physical timeouts that
could lead to either premature removals of partitions when they are
still operating; or slow convergence where processes wrongly believe
they belong to a partition that was removed. On the opposite,
Section~\ref{sec:experimentation} shows that \NAME quickly converges
to consistent partitioning even in large scale networks.

>>>>

Content indexing services in geo-distributed infrastructures allow
\processes to retrieve specific content while leveraging the
advantages of replication. These systems mostly rely on dedicated
location services host by possibly remote third-party \processes; and
cutting out the middleman requires that each \process maintains its
own index in a decentralized fashion.
% This section reviews these
% approaches.

@@

\item [Fully decentralized:]

Cutting out the middleman by hosting a location service on each and
every \process improves response time of content retrieval. However,
it still requires every \process to index every live replica as well
as their respective distance in order to rank them.
%% The opposite approach consists in hosting the index directly on the
%% nodes, avoiding any prior request to access a content.
\underline{N}amed \underline{D}ata \underline{N}etworking
(NDN)~\cite{nlsr} broadcasts information about cache updates to all
\nodes in the system. Having the entire knowledge of all the replica
locations along with distance information carried into messages, each
\node easily determine where the closest copy of specific content
resides, without contacting any remote
service. \underline{C}onflict-\underline{f}ree \underline{r}eplicated
\underline{d}atatype (CRDT)~\cite{shapiro2011crdts} for set data
structures could also implement such a location service. \Processes
would eventually have a set of all replicas, assuming eventual
delivery of messages.
\noindent Such solutions inherently imply that every \process receives
every message, which contradicts with the principles of Edge
infrastructures that aim at reducing the volume of data passing
through the network. On the opposite, each \process running \NAME only
registers its closest replica. This allows \NAME to use scoped
broadcast as a communication primitive to lock down the traffic
generated by content indexing based on distances.
% Such solutions inherently imply that every node will
% eventually receive all messages, contrary to \NAME.

\item [Scoped flooding:]

Some state-of-the-art approaches also confine the dissemination of
information to interested \processes based on distance. 
% \item [Membership protocols:]

\noindent Distance-based membership protocols such as
T-Man~\cite{t-man} make \processes converge to a specific network
topology depending on targeted properties. They periodically
communicate with their neighbors to compare their state. Following
this exchange, they add and remove communication links to other
\processes. Over exchanges, they converge towards a topology ensuring
the targeted properties.  While at first glance membership protocols
and \NAME could share common preoccupations, \NAME does not aim at
building any topology and never modifies neighbors of \processes.

%% In
%% addition, distance-based membership protocols often rely on random
%% peer-sampling protocols to avoid falling in a local minimum that would
%% stop them from reaching this targeted topology. This contradicts with
%% the principles of Edge infrastructures as well, in a minor way.

%% At first glance, membership protocols~\cite{t-man} would appear to
%% provide suitable abstractions to create a scope-related
%% partitioning, as proposed in this paper. Such protocols usually
%% rely on gossip mechanisms, implying contacts with random nodes that
%% can be far away in the physical topology.  They are mostly
%% implemented by modifying the neighboring of a given node according
%% to a certain metric in a logical overlay.

%% These protocols are usually cycle-based, meaning that they impose a
%% constant load on the network traffic, even when the system state does
%% not change. \NAME only generates traffic upon system changes.

\noindent The most closely related approaches to \NAME come from
\underline{i}nformation-\underline{c}entric \underline{n}etworking
(ICN)~\cite{garcia-lopez, hemmati2015namebased}. They periodically
advertise their cache content, and advertisements stop as soon as they
reach uninterested \processes. However their operation requires that
\begin{inparaenum}[(i)]
\item they constantly generate traffic even in quiescent systems where
  \processes do not add nor destroy replicas; and 
\item they define physical-clock-based timeouts the value of which
  depends on network topology properties such as network diameter.
  %also incur an overhead even in quiet contexts without any update.
  % Moreover, they necessarily rely on physical timeouts
  Unfitting timeouts lead to premature removals of live replicas; or
  slow convergence where \processes wrongly believe that their closest
  replica is live while it was destroyed.
\end{inparaenum}
On the opposite, \NAME quickly inform each \process of their closest
replica even in large networks; and when the system becomes quiescent,
\NAME has no overhead.
